### 2025-04-18 index.qmd
20250417 - robust regression

# Automatically create a bib database for R packages
packagesForBibliography <- c(
  "petersenlab", "ffanalytics",
  "knitr", "rmarkdown", "dplyr", "ggplot2", "tidyverse", "downlit", "xml2",
  "nflreadr", "nflplotR", "nflfastR", "nfl4th", "gsisdecoder", "progressr",
  "DescTools", "pwr", "pwrss", "WebPower", "XICOR", "dagitty", "ggdag",
  "lubridate", "ggtext", "gghighlight", "ggExtra", "grid", "patchwork", "pROC",
  "lme4", "lmerTest", "MuMIn", "emmeans", "pbkrtest", "sjstats", "AICcmodavg",
  "rstan", "brms", "bbmle", "fitdistrplus", "mclust", "magrittr", "viridis",
  "plotly", "quantmod", "fPortfolio", "xts", "zoo", "forecast", "stringi", #"webshot2", 
  "parallel", "parallelly", "doParallel", "missRanger", "ggridges", "powerjoin",
  "caret", "gpboost", "cmdstanr", "learnr", "remotes", "corrplot", "correlation", 
  "mgcv", "rms", "car", "performance", "lavaan", "mice", "miceadds"
)

>>>>

# Automatically create a bib database for R packages
packagesForBibliography <- c(
  "petersenlab", "ffanalytics",
  "knitr", "rmarkdown", "dplyr", "ggplot2", "tidyverse", "downlit", "xml2",
  "nflreadr", "nflplotR", "nflfastR", "nfl4th", "gsisdecoder", "progressr",
  "DescTools", "pwr", "pwrss", "WebPower", "XICOR", "dagitty", "ggdag",
  "lubridate", "ggtext", "gghighlight", "ggExtra", "grid", "patchwork", "pROC",
  "lme4", "lmerTest", "MuMIn", "emmeans", "pbkrtest", "sjstats", "AICcmodavg",
  "rstan", "brms", "bbmle", "fitdistrplus", "mclust", "magrittr", "viridis",
  "plotly", "quantmod", "fPortfolio", "xts", "zoo", "forecast", "stringi", #"webshot2", 
  "parallel", "parallelly", "doParallel", "missRanger", "ggridges", "powerjoin",
  "caret", "gpboost", "cmdstanr", "learnr", "remotes", "corrplot", "correlation", 
  "mgcv", "rms", "car", "performance", "lavaan", "mice", "miceadds","interactions",
  "shiny","PearsonDS","robustbase"
)

### 2025-04-18 multiple-regression.qmd
20250417 - robust regression

```{r}
library("petersenlab")
library("rms")
library("car")
library("caret")
library("lme4")
library("performance")
library("lavaan")
library("mice")
library("miceadds")
library("interactions")
library("brms")
library("tidyverse")
library("knitr")
```

@@

dataToImpute <- player_stats_seasonal %>% 
  filter(position %in% c("WR")) %>% 
  select(player_id, where(is.numeric)) %>% 
  select(
    player_id:games, carries:wopr, fantasy_points, fantasy_points_ppr,
    rush_40_yds, rec_40_yds, fumbles, two_pts, return_yds,
    rush_100_yds:draftround, height:target_share_log) %>% 
  select(-c(fantasy_points_ppr, ageCentered20, target_share_log)) # drop collinear variables

@@

fimlRegression_fit <- lavaan::sem(
  fimlRegression_syntax,
  data = player_stats_seasonal,
  missing = "ML",
  fixed.x = FALSE
)

@@

```{r}
player_stats_seasonal_subset <- player_stats_seasonal %>% 
  filter(!is.na(player_id))

rms::robcov(rms::ols(
  fantasyPoints_transformed ~ age + height + weight + target_share_log,
  data = player_stats_seasonal_subset,
  x = TRUE,
  y = TRUE),
  cluster = player_stats_seasonal_subset$player_id) #account for nested data within player
```

@@

>>>>

```{r}
library("petersenlab")
library("rms")
library("car")
library("caret")
library("lme4")
library("performance")
library("lavaan")
library("mice")
library("miceadds")
library("interactions")
library("brms")
library("robustbase")
library("tidyverse")
library("knitr")
```

@@

dataToImpute <- player_stats_seasonal %>% 
  filter(position %in% c("WR")) %>% 
  select(player_id, position, where(is.numeric)) %>% 
  select(
    player_id:games, carries:wopr, fantasy_points, fantasy_points_ppr,
    rush_40_yds, rec_40_yds, fumbles, two_pts, return_yds,
    rush_100_yds:draftround, height:target_share_log) %>% 
  select(-c(fantasy_points_ppr, ageCentered20, target_share_log)) # drop collinear variables

@@

fimlRegression_fit <- lavaan::sem(
  fimlRegression_syntax,
  data = player_stats_seasonal %>% filter(position %in% c("WR")),
  missing = "ML",
  fixed.x = FALSE
)

@@

```{r}
player_stats_seasonal_subset <- player_stats_seasonal %>% 
  filter(!is.na(player_id)) %>% 
  filter(position %in% c("WR"))

rms::robcov(rms::ols(
  fantasyPoints_transformed ~ age + height + weight + I(log(target_share + 1)),
  data = player_stats_seasonal_subset,
  x = TRUE,
  y = TRUE),
  cluster = player_stats_seasonal_subset$player_id) #account for nested data within player
```

@@

### Robust Regression {#sec-multipleRegressionRobustRegression}

To address outliers, there are various approaches to robust regression.
One approach is to use an MM-type estimator, such as is used in the `lmrob()` and `glmrob()` functions of the `robustbase` package [@R-robustbase; @Todorov2009_packages].

```{r}
robustRegression <- lmrob(
  fantasyPoints_transformed ~ age + height + weight + I(log(target_share + 1)),
  data = player_stats_seasonal %>% filter(position %in% c("WR"))
)

summary(robustRegression)
```
